\documentclass[12pt]{article}
\title{3.1 External Interface Requirements}
\author{Ntiko Mathaba}

\begin{document}
\pagenumbering{roman}
	\section{External Interface Requirements}
		\subsection{System Interfaces}
		The system is going to transform the information the user enters to output the directions to the users final destination. The system will then measure the distance in meters/kilometers and it will also estimate how long it will take the user to reach the final destination from the current location. The system will save the users input so that the user is able to search from history.
		
		\subsection{User Interfaces}
		The user is going to enter the information using a keyboard. The user will be able to instruct the system using this input. The system should be able to enter new information according to the users preferences and interests.The system should provide the user with different routes to the final destination. It should have a short route to the final destination and a route that will go through the users preferences and interests. All of this will be ouputted to the users device screen.
		
		\subsection{Hardware Interfaces}
		The hardware interface is the device the user is going to be using when using NavUP. The device that the user will be using should have GPS Hardware and Wifi Hardware.The system is going to use the GPS hardware to navigate to the destination of the user. This is going to allow the system to determine the location of the user whether its indoors or outdoors. The Wifi Hardware is going to be used to connect to Wifi Routers that are made available all over campus.

		\subsection{Software Interfaces}
		NavUP is going to be a mobile application that uses GPS Maps Software on the smart device of the user as well as the Wifi Software extension. The Maps software is going to be used to manipulate the data entered by the user.
\end{document}